---
title: "WaterMicrobiomeCorrelation"
output: html_document
date: '2022-09-16'
---

```{r}
library(qiime2R); library(phyloseq); library(ggplot2); library(fantaxtic)
ps.dat <- qza_to_phyloseq(features="/storage/microbiome/MicrobiomeWaterCorrelation/Jacint_16S/merged_feature_table.qza",
                taxonomy="/storage/microbiome/MicrobiomeWaterCorrelation/Jacint_16S/merged_taxonomy.qza",
                tree="/storage/microbiome/MicrobiomeWaterCorrelation/Jacint_16S/rooted.tre.qza",
                metadata="/storage/microbiome/MicrobiomeWaterCorrelation/Jacint_16S/merged_metadata.txt")

ps.dat <- name_na_taxa(ps.dat, include_rank = F, na_label="Unknown <tax>")
ps.dat <- tax_glom(ps.dat, taxrank = "Genus")
ps.dat <- label_duplicate_taxa(ps.dat, tax_level="Genus")
taxa_names(ps.dat) <- tax_table(ps.dat)[,6]

ps.dat <- subset_samples(ps.dat, sample_sums(ps.dat)>1000)
sample_names(ps.dat) <- gsub("water2020","water",as.character(sample_data(ps.dat)$samples))
```

# Ordination
```{r}
library(ggpubr); library(ggpmisc)

ps.dat <- subset_taxa(ps.dat, !Genus%in%c("Chloroplast", "Mitochondria"))
ps_rarefied <- rarefy_even_depth(ps.dat, rngseed = TRUE)

phyloseq.water <- subset_samples(ps_rarefied, Type=="water")
phyloseq.polyps <- subset_samples(ps_rarefied, Type=="polyp")

ps_comp <- microbiome::transform(ps_rarefied, "compositional")
ord.bray <- ordinate(ps_comp, method="NMDS", distance="bray")
ord.jaccard <- ordinate(ps_comp, method="NMDS", distance="jaccard",binary=T)
ord.wunifrac <- ordinate(ps_comp, method="NMDS", distance="wunifrac")
ord.unifrac <- ordinate(ps_comp, method="NMDS", distance="unifrac")

n1 <- plot_ordination(ps_comp, ord.bray, type="samples",shape="Type",color="Population")+
  theme_bw()+geom_point(size=3)+labs(title="Bray-Curtis")+
  scale_shape_manual(values=c("polyp"=1, "water"=17))+theme(legend.box.just = "center")
n2 <- plot_ordination(ps_comp, ord.jaccard, type="samples",shape="Type",color="Population")+
  theme_bw()+geom_point(size=3)+labs(title="Jaccard presence-absence")+
  scale_shape_manual(values=c("polyp"=1, "water"=17))+theme(legend.box.just = "center")
n3 <- plot_ordination(ps_comp, ord.wunifrac, type="samples",shape="Type",color="Population")+
  theme_bw()+geom_point(size=3)+labs(title="Weighted UniFrac")+
  scale_shape_manual(values=c("polyp"=1, "water"=17))+theme(legend.box.just = "center")
n4 <- plot_ordination(ps_comp, ord.unifrac, type="samples",shape="Type",color="Population")+
  theme_bw()+geom_point(size=3)+labs(title="Unweighted UniFrac")+
  scale_shape_manual(values=c("polyp"=1, "water"=17))+theme(legend.box.just = "center")

#ragg::agg_png(file="/storage/microbiome/MicrobiomeWaterCorrelation/MS/nmds_rarefied.png",
#                 width=2000, height=2000, res=300)
pdf(file="/storage/microbiome/MicrobiomeWaterCorrelation/MS/nmds_rarefied.pdf",
                 width=7, height=7)
ggarrange(n1,n2,n3,n4, nrow=2, ncol=2, common.legend=T, labels="AUTO")
dev.off()

dist.bray <- phyloseq::distance(ps_rarefied, method="bray")
dist.jaccard <- phyloseq::distance(ps_rarefied, method="jaccard",binary=T)
dist.wunifrac <- phyloseq::distance(ps_rarefied, method="wunifrac")
dist.unifrac <- phyloseq::distance(ps_rarefied, method="unifrac")

sampledf <- data.frame(sample_data(ps_rarefied))

a.bray <- vegan::adonis2(dist.bray~Type*Population, data=sampledf)
a.jaccard <- vegan::adonis2(dist.jaccard~Type*Population, data=sampledf)
a.wunifrac <- vegan::adonis2(dist.wunifrac~Type*Population, data=sampledf)
a.unifrac <- vegan::adonis2(dist.unifrac~Type*Population, data=sampledf)

table.bray <- data.frame(Variable=c("Type","Population",
                                    "Type:Population","Residual","Total"),
                         R2=round(a.bray$R2,2), p=round(a.bray$`Pr(>F)`,3))
table.bray$p[is.na(table.bray$p)] <- ""
table.jaccard <- data.frame(Variable=c("Type","Population",
                                    "Type:Population","Residual","Total"),
                         R2=round(a.jaccard$R2,2), p=round(a.jaccard$`Pr(>F)`,3))
table.jaccard$p[is.na(table.jaccard$p)] <- ""
table.wunifrac <- data.frame(Variable=c("Type","Population",
                                    "Type:Population","Residual","Total"),
                         R2=round(a.wunifrac$R2,2), p=round(a.wunifrac$`Pr(>F)`,3))
table.wunifrac$p[is.na(table.wunifrac$p)] <- ""
table.unifrac <- data.frame(Variable=c("Type","Population",
                                    "Type:Population","Residual","Total"),
                         R2=round(a.unifrac$R2,2), p=round(a.unifrac$`Pr(>F)`,3))
table.unifrac$p[is.na(table.unifrac$p)] <- ""

#ragg::agg_png(file="/storage/microbiome/MicrobiomeWaterCorrelation/MS/nmds_rarefied_stats.png", width=3000, height=3000, res=300)
pdf(file="/storage/microbiome/MicrobiomeWaterCorrelation/MS/nmds_rarefied_stats.pdf", width=10, height=10)
ggarrange(
  n1+annotate(geom="table", x=2,y=-2.1, label=list(table.bray),hjust=0.95,vjust=0.2),
  n2+annotate(geom="table", x=2,y=-2, label=list(table.jaccard),hjust=0.95,vjust=0.1),
  n3+annotate(geom="table", x=0.65,y=-0.7, label=list(table.wunifrac),hjust=0.95,vjust=0.1),
  n4+annotate(geom="table", x=0.6,y=-0.6, label=list(table.unifrac),hjust=0.95,vjust=0.1),
    nrow=2, ncol=2, common.legend=T, labels="AUTO")
dev.off()

ggsave(plot = n1 + scale_color_discrete(guide="none")+theme(plot.title=element_blank()), 
       file = "/storage/microbiome/MicrobiomeWaterCorrelation/MS/nmds_Bray.pdf",
       width=7, height=5)
```

```{r}
library(readxl)
library(rnaturalearth)
library(rnaturalearthdata)

coords <- read_excel("/storage/microbiome/MicrobiomeWaterCorrelation/pop_coordinates.xlsx")
coords$Coordinates <- gsub("\n| ", "", coords$Coordinates)
coords$N <- as.numeric(gsub("N","",sapply(strsplit(coords$Coordinates, split=";"),"[",1)))
coords$E <- as.numeric(gsub("E","",sapply(strsplit(coords$Coordinates, split=";"),"[",2)))

europe_shoreline <- ne_coastline(scale = "medium", returnclass = "sf")
hungary <- ne_countries(country = "Hungary", returnclass = "sf", scale="large")

rectangle <- data.frame(
  xmin = 19, xmax = 22.7,
  ymin = 45.75, ymax = 48.5)

europe_hungary_inset <- ggplot() +
  geom_sf(data = europe_shoreline, color = "black") +
  geom_sf(data = hungary, fill = "red", color = "red") +
  coord_sf(xlim=c(-10,40),ylim=c(30,70))+
  geom_rect(data = rectangle, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill = NA, color = "black")+theme_bw()

ggplot() +
  geom_point(data = coords, aes(x = E, y = N, color = `Population ID`),size=4) +
  # Add Hungary borders
  geom_sf(data = hungary, fill = NA, color = "red") +
  # Set plot limits to focus on Hungary
  coord_sf(xlim = c(19, 22.7), ylim = c(45.75, 48.5))+
  annotation_custom(ggplotGrob(europe_hungary_inset), xmin = 21.5, xmax = Inf, ymin = 45.5, ymax = Inf)

names(coords)[1] <- "PopID"

```


# Correlation between water-polyp microbiota composition
Mantel test - for this, the distance between multiple polyp samples from the same site are averaged 

- both of these analyses are done on the following distance matrices:
## Weighted Unifrac

```{r Mantel test weighted Unifrac}
library(qiime2R); library(broom); library(ape); library(phyloseq)
library(ggrepel); library(ape); library(dplyr); library(ggpubr)

w.data <- sample_data(phyloseq.water)
w.data$samples <- gsub("water2020","water",w.data$samples)
w.mat <- as.matrix(distance(phyloseq.water, "wunifrac"))

sites <- gsub("/water$","",w.data$samples)

p.data <- sample_data(phyloseq.polyps)
p.mat <- as.matrix(distance(phyloseq.polyps, "wunifrac"))

wp <- matrix(0, ncol=ncol(p.mat), nrow=nrow(w.mat), 
             dimnames=list(row.names(w.mat),colnames(p.mat)))
for(i in 1:nrow(wp)){
  wp[i,][(gsub("/water$","",row.names(wp)[i])==gsub("/[0-9]+$","",colnames(wp)))]<-1
}

pp.mat <- matrix(NA, ncol=ncol(w.mat),nrow=nrow(w.mat), dimnames=dimnames(w.mat))
for(i in 1:nrow(pp.mat)){
  for(j in 1:ncol(pp.mat)){
    from<-gsub("/water$","",row.names(pp.mat)[i])
    to<-gsub("/water$","",colnames(pp.mat)[j])
      site.mat <- p.mat[gsub("/[0-9]+$","",row.names(p.mat))==from, 
                   gsub("/[0-9]+$","",colnames(p.mat))==to]
    if(identical(from, to)){
      pp.mat[i,j]<-mean(site.mat[upper.tri(site.mat)])
    } else {
      pp.mat[i,j]<-mean(site.mat)
    }
  }
}

mantel.test.weightedUnifrac <- mantel.test(w.mat, pp.mat, graph=F)
mantel.weightedUnifrac <- data.frame(water.dist = w.mat[upper.tri(w.mat)], polyp.dist=pp.mat[upper.tri(pp.mat)], type="weighted Unifrac")
```
## Unweighted Unifrac

```{r Mantel test unweighted Unifrac}
w.data <- sample_data(phyloseq.water)
w.data$samples <- gsub("water2020","water",w.data$samples)
w.mat <- as.matrix(distance(phyloseq.water, "unifrac"))

sites <- gsub("/water$","",w.data$samples)

p.data <- sample_data(phyloseq.polyps)
p.mat <- as.matrix(distance(phyloseq.polyps, "unifrac"))

wp <- matrix(0, ncol=ncol(p.mat), nrow=nrow(w.mat), 
             dimnames=list(row.names(w.mat),colnames(p.mat)))
for(i in 1:nrow(wp)){
  wp[i,][(gsub("/water$","",row.names(wp)[i])==gsub("/[0-9]+$","",colnames(wp)))]<-1
}

pp.mat <- matrix(NA, ncol=ncol(w.mat),nrow=nrow(w.mat), dimnames=dimnames(w.mat))
for(i in 1:nrow(pp.mat)){
  for(j in 1:ncol(pp.mat)){
    from<-gsub("/water$","",row.names(pp.mat)[i])
    to<-gsub("/water$","",colnames(pp.mat)[j])
      site.mat <- p.mat[gsub("/[0-9]+$","",row.names(p.mat))==from, 
                   gsub("/[0-9]+$","",colnames(p.mat))==to]
    if(identical(from, to)){
      pp.mat[i,j]<-mean(site.mat[upper.tri(site.mat)])
    } else {
      pp.mat[i,j]<-mean(site.mat)
    }
  }
}

mantel.test.unweightedUnifrac <- mantel.test(w.mat, pp.mat, graph=F)
mantel.unweightedUnifrac <- data.frame(water.dist = w.mat[upper.tri(w.mat)], polyp.dist=pp.mat[upper.tri(pp.mat)], type="unweighted Unifrac")
```
## Bray-Curtis

```{r Bray-Curtis}
w.data <- sample_data(phyloseq.water)
w.data$samples <- gsub("water2020","water",w.data$samples)
w.mat <- as.matrix(distance(phyloseq.water, "bray"))

sites <- gsub("/water$","",w.data$samples)

p.data <- sample_data(phyloseq.polyps)
p.mat <- as.matrix(distance(phyloseq.polyps, "bray"))

wp <- matrix(0, ncol=ncol(p.mat), nrow=nrow(w.mat), 
             dimnames=list(row.names(w.mat),colnames(p.mat)))
for(i in 1:nrow(wp)){
  wp[i,][(gsub("/water$","",row.names(wp)[i])==gsub("/[0-9]+$","",colnames(wp)))]<-1
}

pp.mat <- matrix(NA, ncol=ncol(w.mat),nrow=nrow(w.mat), dimnames=dimnames(w.mat))
for(i in 1:nrow(pp.mat)){
  for(j in 1:ncol(pp.mat)){
    from<-gsub("/water$","",row.names(pp.mat)[i])
    to<-gsub("/water$","",colnames(pp.mat)[j])
      site.mat <- p.mat[gsub("/[0-9]+$","",row.names(p.mat))==from, 
                   gsub("/[0-9]+$","",colnames(p.mat))==to]
    if(identical(from, to)){
      pp.mat[i,j]<-mean(site.mat[upper.tri(site.mat)])
    } else {
      pp.mat[i,j]<-mean(site.mat)
    }
  }
}

mantel.test.braycurtis <- mantel.test(w.mat, pp.mat, graph=F)
mantel.braycurtis <- data.frame(water.dist = w.mat[upper.tri(w.mat)], polyp.dist=pp.mat[upper.tri(pp.mat)], type="Bray-Curtis")
```
## Jaccard

```{r Jaccard}
w.data <- sample_data(phyloseq.water)
w.data$samples <- gsub("water2020","water",w.data$samples)
w.mat <- as.matrix(distance(phyloseq.water, "jaccard", binary=T))

sites <- gsub("/water$","",w.data$samples)

p.data <- sample_data(phyloseq.polyps)
p.mat <- as.matrix(distance(phyloseq.polyps, "jaccard", binary=T))

wp <- matrix(0, ncol=ncol(p.mat), nrow=nrow(w.mat), 
             dimnames=list(row.names(w.mat),colnames(p.mat)))
for(i in 1:nrow(wp)){
  wp[i,][(gsub("/water$","",row.names(wp)[i])==gsub("/[0-9]+$","",colnames(wp)))]<-1
}

pp.mat <- matrix(NA, ncol=ncol(w.mat),nrow=nrow(w.mat), dimnames=dimnames(w.mat))
for(i in 1:nrow(pp.mat)){
  for(j in 1:ncol(pp.mat)){
    from<-gsub("/water$","",row.names(pp.mat)[i])
    to<-gsub("/water$","",colnames(pp.mat)[j])
      site.mat <- p.mat[gsub("/[0-9]+$","",row.names(p.mat))==from, 
                   gsub("/[0-9]+$","",colnames(p.mat))==to]
    if(identical(from, to)){
      pp.mat[i,j]<-mean(site.mat[upper.tri(site.mat)])
    } else {
      pp.mat[i,j]<-mean(site.mat)
    }
  }
}

mantel.test.jaccard <- mantel.test(w.mat, pp.mat, graph=F)
mantel.jaccard <- data.frame(water.dist = w.mat[upper.tri(w.mat)], polyp.dist=pp.mat[upper.tri(pp.mat)], type="Jaccard")
```

Plot matrix correlation

```{r}
library(ggplot2)
df <- rbind(mantel.weightedUnifrac, mantel.unweightedUnifrac, mantel.braycurtis, mantel.jaccard)
df$type <- factor(df$type, levels=c("Jaccard","Bray-Curtis", "unweighted Unifrac", "weighted Unifrac"))

mantel.res <- data.frame(z=c(mantel.test.jaccard$z.stat, 
                             mantel.test.braycurtis$z.stat,
                             mantel.test.unweightedUnifrac$z.stat,
                             mantel.test.weightedUnifrac$z.stat),
                         p=c(mantel.test.jaccard$p, 
                             mantel.test.braycurtis$p,
                             mantel.test.unweightedUnifrac$p,
                             mantel.test.weightedUnifrac$p),
                         type=factor(c("Jaccard","Bray-Curtis", "unweighted Unifrac", "weighted Unifrac")))

dat.text <- data.frame(label=paste("Mantel p =", mantel.res$p),
                       type=factor(c("Jaccard","Bray-Curtis", "unweighted Unifrac", "weighted Unifrac")))

#ragg::agg_png(file="/storage/microbiome/MicrobiomeWaterCorrelation/MS/matrix_correlation.png",
#                 width=1800, height=1200, res=300)
pdf(file="/storage/microbiome/MicrobiomeWaterCorrelation/MS/matrix_correlation.pdf",
                 width=6, height=4)

ggplot(df, aes(x=water.dist, y=polyp.dist))+geom_point(alpha=0.5)+
  facet_wrap(~type)+theme_bw()+
  xlab("Distance between water samples")+ylab("Distance between polyp samples")+
  ylim(0.25,1.4)+
  geom_text(
  data    = dat.text,
  mapping = aes(x = -Inf, y = -Inf, label = label), color="red",
  hjust   = -0.1,
  vjust   = -12
)

dev.off()
  
```


# Sloan neutral model
- plotting the relationship between mean abundance of an OTU across samples vs. the probability of being observed 

```{r}
library(ggplot2); library(ggpubr); library(ggrepel); library(dplyr)

water.table <- otu_table(subset_samples(ps_rarefied, Type=="water"))
polyp.table <- otu_table(subset_samples(ps_rarefied, Type=="polyp"))

water.relAbund <- prop.table(water.table, 2)
water.meanAbund<-apply(water.relAbund, 1, mean)
water.Occurrence<-apply(water.table>0,1,sum)/ncol(water.table)

polyps.relAbund<-prop.table(polyp.table, 2)
polyps.meanAbund<-apply(polyps.relAbund, 1, mean)
polyps.Occurrence<-apply(polyp.table>0,1,sum)/ncol(polyp.table)

sloan<-(data.frame(Abund=polyps.meanAbund, Occurrence=polyps.Occurrence, 
                  genus=taxa_names(ps_rarefied)))
sloan<-sloan[sloan$Abund>0,]
m<-glm(Occurrence~log10(Abund), data=sloan, family="quasibinomial")
sloan$resid <- resid(m)
sloan$resid_bin <- ifelse(sloan$resid>0,"positive","negative")

p1 <- ggplot(sloan, aes(y=Occurrence, x=log10(Abund)))+geom_point()+
  xlab(bquote(~Log[10] ~ "Abundance on polyps"))+
  ylab("Occurrence on polyps")+
  geom_smooth(method="glm",method.args=list(family="quasibinomial"))+
  geom_text_repel(
    data=subset(sloan, resid<quantile(resid, 0.025) | 
                  resid>quantile(resid, 0.975)),
    aes(label=genus,color=resid_bin),size=3,
    box.padding = unit(0.35, "lines"),
    point.padding = unit(0.3, "lines")
  ) + theme_bw()+theme(legend.position = "top")+
  scale_color_manual(values=c("positive"="forestgreen","negative"="red"),name="",
                     labels=c("Over-represented taxa","Under-represented taxa"))

x <- data.frame(taxon=names(resid(m)), neutrality = resid(m))
row.names(x)<-NULL

y <- data.frame(taxon=names(water.meanAbund), waterAbund = water.meanAbund)
row.names(y) <- NULL

z <- data.frame(taxon=names(water.Occurrence), waterPrev = water.Occurrence)
row.names(z) <- NULL

xy <- left_join(x, y, by="taxon")
xyz <- left_join(xy, z, by="taxon")

p2 <- ggplot(xyz, aes(x=waterPrev, y=neutrality))+geom_point()+geom_smooth(method="lm")+
  theme_bw()+ xlab("Occurrence in water samples")+
  ylab("Departures from neutrality on polyps")+
  scale_y_continuous(breaks=c(-1,0.5),labels=c("Under-represented","Over-represented"))+
  theme(axis.text.y = element_text(angle=90, hjust=0.5))

p3 <- ggplot(xyz, aes(x=log10(waterAbund), y=neutrality))+geom_point()+geom_smooth(method="lm")+
  theme_bw()+ xlab(bquote(~Log[10] ~ "Abundance in water samples"))+
  ylab("Departures from neutrality on polyps")+
  scale_y_continuous(breaks=c(-1,0.5),labels=c("Under-represented","Over-represented"))+
  theme(axis.text.y = element_text(angle=90, hjust=0.5))

cor.test(xyz$waterPrev, xyz$neutrality, method="s")
cor.test(xyz$waterAbund, xyz$neutrality, method="s")

#ragg::agg_png("/storage/microbiome/MicrobiomeWaterCorrelation/MS/neutrality_rarefied_red.png",
#              res=300, width=1800, height=1800, scaling=0.7)
pdf("/storage/microbiome/MicrobiomeWaterCorrelation/MS/neutrality_rarefied_red.pdf", width=8, height=8)
ggarrange(p1,ggarrange(p2,p3,nrow=1,labels=c("B","C")),nrow=2,labels=c("A","",""))
#ggarrange(p1,p2+ylab("Departures from neutrality"), nrow=2, heights = c(2,1), 
#          labels="AUTO", vjust=1)
dev.off()
```

```{r}
library(NetCoMi); library(cowplot); library(ggraph); library(tidygraph); library(grafify);
library(igraph); library(scatterpie); library(ggforce); library(ggnewscale)
if(FALSE){
net_spring <- netConstruct(subset_samples(ps_rarefied,Type=="polyp"),
                           filtTax = "highestFreq",
                           filtTaxPar = list(highestFreq = 50),
                           #filtSamp = "totalReads",
                           #filtSampPar = list(totalReads = 1000),
                           measure = "spring",
                           measurePar = list(nlambda=10, 
                                             rep.num=10),
                           normMethod = "none", 
                           zeroMethod = "none",
                           sparsMethod = "none", 
                           dissFunc = "signed",
                           verbose = 2,
                           seed = 123456)
}

sel_tax <- union(
  top_taxa(subset_samples(ps_rarefied, Type=="polyp"),n=30)$top_taxa[,2],
  top_taxa(subset_samples(ps_rarefied, Type=="water"),n=30)$top_taxa[,2]
  )

ps_sel <- subset_taxa(ps_rarefied, Genus%in%sel_tax)

net_spring <- netConstruct(data = ps_sel,
                           #jointPrepro = FALSE,
                           #filtTax = "highestFreq",
                           #filtTaxPar = list(highestFreq = 50),
                           #filtSamp = "totalReads",
                           #filtSampPar = list(totalReads = 1000),
                           measure = "spring",
                           measurePar = list(nlambda=10, 
                                             rep.num=10),
                           normMethod = "none", 
                           zeroMethod = "none",
                           sparsMethod = "none", 
                           dissFunc = "signed",
                           verbose = 2,
                           seed = 123456)

props_spring <- netAnalyze(net_spring, 
                           centrLCC = TRUE,
                           clustMethod = "cluster_fast_greedy",
                           hubPar = "eigenvector",
                           weightDeg = FALSE, normDeg = FALSE)
p <- plot(props_spring, 
          nodeColor = "cluster", 
          nodeSize = "eigenvector",
          nodeSizeSpread = 2,
          cexNodes = 4,
          showTitle = FALSE,
          labelScale = TRUE,
          cexLabels = 5)

if(FALSE){ ## using this to check that abundance values on the network graph pie
## chart are correct. That's because the difference between taxa seems much higher 
## there due to lack of log-transformation
  water.abund <- taxa_sums(subset_samples(ps_sel, Type=="water"))%>%data.frame()%>%
  tibble::rownames_to_column()%>%rename_with(~c("taxon","abund"), everything())%>%
  mutate(type="water")
polyp.abund <- taxa_sums(subset_samples(ps_sel, Type=="polyp"))%>%data.frame()%>%
  tibble::rownames_to_column()%>%rename_with(~c("taxon","abund"), everything())%>%
  mutate(type="polyp")
all.abund <- rbind(water.abund, polyp.abund) %>%
  mutate(cluster = as.factor(props_spring$clustering$clust1[all.abund$taxon]))

ggplot(all.abund, aes(y=(abund), x=type, fill=cluster))+geom_boxplot()+facet_wrap(~cluster)+
  ylim(0,50000)+geom_jitter()
ggplot(all.abund, aes(y=log10(abund), x=type, fill=cluster))+geom_boxplot()+facet_wrap(~cluster)+
  geom_jitter()
}

plot_graph <- as_tbl_graph(graph_from_adjacency_matrix(net_spring$adjaMat1,weighted=T,mode="undirected"))

node.list <- plot_graph%>%activate(nodes)%>%data.frame()%>%as.vector()
node.data <- data.frame(node=node.list$name,
                        Cluster=as.factor(props_spring$clustering$clust1[node.list$name]),
                        water.abund=taxa_sums(subset_samples(ps_sel, Type=="water"))[node.list$name],
                        polyp.abund=taxa_sums(subset_samples(ps_sel, Type=="polyp"))[node.list$name])
plot_graph <- plot_graph%>%activate(nodes)%>%left_join(node.data, by=c("name"="node"))

V(plot_graph)$w <- taxa_sums(subset_samples(ps_sel, Type=="water"))[node.list$name]
V(plot_graph)$p <- taxa_sums(subset_samples(ps_sel, Type=="polyp"))[node.list$name]
V(plot_graph)$grp <- props_spring$clustering$clust1[node.list$name]
plot_graph2 <- delete_vertices(plot_graph,"Candidatus_Finniella")

set.seed(123)
xy <- layout_with_kk(plot_graph2)#, weights=0.1*E(plot_graph2)$weight)
V(plot_graph2)$x <- xy[,1]
V(plot_graph2)$y <- xy[,2]
V(plot_graph2)$Cluster <- as.factor(V(plot_graph2)$grp)
plot_graph2 <- as_tbl_graph(plot_graph2)

net <- ggraph(plot_graph2, "manual", x = V(plot_graph)$x, y = V(plot_graph)$y)+
  geom_edge_fan(color="grey")+theme_graph()+

  geom_mark_hull(aes(x,y,group=Cluster,fill=Cluster),
                       concavity=8,alpha=0.25,linetype=2)+
  scale_fill_grafify(name="Cluster:",palette="fishy")+
  new_scale_fill()+    
  geom_scatterpie(cols=c("p","w"),color=NA,
                  data=as.data.frame(plot_graph2, "vertices"))+
  scale_fill_manual(name="Type:",values=c("w"="lightblue3","p"="orange"),
                    labels=c("w"="water","p"="polyp"))+
  geom_node_text(aes(label=name,size=2*log10(water.abund+polyp.abund)),
                 repel=T,force=25,force_pull=0)+guides(size="none")

ggsave(file="/storage/microbiome/MicrobiomeWaterCorrelation/MS/network_rarefied_third_alternative.pdf", width=10, height=8, plot=net,device=cairo_pdf)
```

